method

### 2021-12-06 06_Paper/ER-ED/method.Rmd
corrected ANOVA

library(targets)    # to keep track of all relevant files
library(readxl)     # import excel files
library(here)       # to set directories without defined paths
library(papaja)     # APA conform output
library(afex)       # for ANOVA
library(emmeans)
library(ggplot2)    # for nice plots

@@

  } else if (data_ER$trigger[i] == 25) {

@@

# ANOVA subjective arousal ratings

aov.arousal = afex::aov_ez(id = "ID",
                           dv = "arousal",
                           data = data_ER,
                           within = "block",
                           fun_aggregate = mean) 
afex::nice(aov.arousal, es = "pes")

# compute posthoc tests for within measures
posthoc_arousal = emmeans::emmeans(aov.arousal$aov, specs = "block")
pairs(posthoc_arousal, adjust = "bonferroni")

>>>>

library(targets)    # to keep track of all relevant files
library(readxl)     # import excel files
library(here)       # to set directories without defined paths
library(papaja)     # APA conform output
library(afex)       # for ANOVA
library(emmeans)
library(ggplot2)    # for nice plots
library(dplyr)

@@

  } else if (data_ER$trigger[i] == 26) {

@@

# ANOVA subjective arousal ratings
# View Condition

arousal_view = data_ER %>%
  subset(data_ER$block == "view_neu" | data_ER$block == "view_neg")

aov_arousalView = afex::aov_ez(id = "ID",
                           dv = "arousal",
                           data = arousal_view,
                           within = "block",
                           fun_aggregate = mean) 
afex::nice(aov_arousalView, es = "pes")

# compute posthoc tests for within measures
posthoc_arousalView = emmeans::emmeans(aov_arousalView$aov, specs = "block")
pairs(posthoc_arousalView, adjust = "bonferroni")
